Scikit-learn: machine learning without learning the machinery

### 2014-05-18 article.tex
Iter

@@

    \caption{Wage prediction from years of work experience and education,
    using random forests.}
\end{figure}

>>>>

On Fig.\,\ref{fig:random_forest}, we use a popular machine-learning
algorithm, Random Forests, to try to predict the wage from the years of
education, or the years of work experience, either as separate features,
or combined.

@@

    \caption{Wage prediction from years of work experience and education,
    using random forests.\label{fig:random_forest}}
\end{figure}
